### 2016-02-16 ch05-initvals/initial-values.tex
LM algo rewritten
Timing of initvals completed

\begin{algorithm}
\caption{Levenberg-Marquardt~\citep{Marquardt1963}, \citep[Sec. 9.L.4]{Pintelon2012}}\label{LMalgo}
\begin{algorithmic}[1]
  \Statex Cost function \eqref{eq:MLEcf} is rewritten as $V(\theta) = \epsilon^{\TT} \epsilon$. 
  \Statex The iterations start at $\atIter[0]{\theta} = \theta^{\mathrm{init}}$ and $\lambda = \max(\sigma)/100$.
%\Function{LevenbergMarquardt}{$V(\theta), \atIter[0]{\theta}$}
   \For{$i$ \textbf{in} $1 \to \infty$}
      \State $U \, \Sigma \, W^{\TT} \gets \mathtt{svd}\left( \frac{\partial \epsilon}{\partial \theta}\right)$ with $\mathrm{diag}(\Sigma) = [\sigma_1, \ldots, \sigma_n]$
      % \State \textbf{if} $i=1$ \textbf{ then} $\lambda \gets \max(\sigma) / 100$
      \State $\sigma_k \gets \sigma_k / (\sigma_k^2 + \lambda^2) \quad \forall k \in \{1, \ldots, n\}$
      \State $\delta\theta \gets - W  \Sigma^{\TT}  U^{\TT} \epsilon$
      \State $\atIter[i]{\theta} \gets (\atIter[i-1]{\theta} + \delta\theta) / \norm{\atIter[i-1]{\theta} + \delta\theta} $
      \If{$V(\atIter[i]{\theta}) > V(\atIter[i-1]{\theta})$}
          \State $\lambda \gets 10 \lambda$ and then retry at $i \gets i - 1$
      \Else
          \State $\lambda \gets 0.4 \lambda$
      \EndIf
      \State \textbf{if} $\norm{\delta\theta}/\norm{\atIter[i]{\theta}} < n_{\theta}  \cdot 10^{-6} $ \textbf{then} \textbf{return} $\hat{\theta} \gets \atIter[i]{\theta}$
   \EndFor
%\EndFunction
\end{algorithmic}
\end{algorithm}

@@

%\JL{
The \gls{RFIR} estimator is formulated in the time domain. 
It estimates the impulse response of a discrete time system as the minimizer of the following regularized least squares objective function:
\begin{align}\label{eq:hRFIRdef}
\hat g_{\mathrm{RFIR}} &= \argmin_{g} \norm{y - g \ast u }^2 + \sigma^2 g^{\TT}P^{-1}g
\end{align}
where $g$ is the vectorized impulse response $g(t)$, with $t = 0,1,\cdots,n_h - 1$, assuming that the impulse response is $n_g$ samples long. 
Furthermore, $g\ast u$ is the convolution of $g$ with the input signal $u$, and $P\in \mathbb{R}^{n_g\times n_g}$ is the kernel matrix. 
Note that \eqref{eq:hRFIRdef} is quadratic in $g$, such that $\hat g_{\mathrm{RFIR}}$ can be computed analytically in a single step.
The kernel matrix $P$ embodies prior knowledge on the system to be estimated. 
Here, the \gls{DCkernel} is used. 
Specifically, the element at $t_1,t_2$ of $P$ is given by
\begin{equation}
P(\alpha,\beta)_{t_1,t_2} = e^{-\alpha|t_1 - t_2|}e^{-\beta(t_1 + t_2)/2}
\end{equation}
 for $t_1,t_2 \in \left\{0,1,\cdots,n_h - 1\right\}$ which makes the estimated impulse response to be an exponentially decaying function of $t$ with decay rate $\beta^{-1}$, and correlation length $\alpha^{-1}$. 
 The latter \emph{hyperparameters} $\alpha$ and $\beta$ are determined using Empirical Bayes, i.e. as the maximizers of the \gls{LML} of the measured output signal:
\begin{align}
\mathrm{LML}(y) = -y^{\TT}\Sigma(\alpha,\beta)^{-1}y - \log |\Sigma(\alpha,\beta)| \text{,}
\end{align}
where $\Sigma(\alpha,\beta) = \sigma^2 \I + \phi^{\TT}P(\alpha,\beta)\phi$ and $\phi$ is a Toeplitz matrix constructed with $u$. 
This problem is solved using \code{fmincon} in \MATLAB.

@@

Formally, let $\model{\bullet}$ be the final parametric estimate of the system, where the subscript $\bullet$ denotes the methods (from left to right in Fig.~\ref{fig:flowgraph}) when an initial estimate $\model[init]{\bullet}$ is used, \emph{viz}:
%\comment{JL:be consequent with the orders (and refer to the specific branches in the flowchart)}
\begin{itemize}
\item 
$\model{0}$ via the true model $\true{G}$ as an initial estimate,
\item
$\model{exist}$ is obtained via GTLS and BTLS,
\item
$\model{trunc}$ by the use of the LPM with truncation as an initial estimate,
\item
$\model{RFIR}$, initialized by means of the RFIR method. 
\end{itemize}

@@

\begin{conjecture}\label{conj1}
The true model $\true{G}$ as an initial estimate is the best possible initial estimate one can use for the nonlinear identification algorithm (the leftmost path in \figref{fig:flowgraph}) and will allow the optimization to converge to the \emph{best local optimum}, i.e. $\model{0}$.
\end{conjecture}
\begin{remark}
The use of $\true{G}$ as an initial estimation not necessarily entails in converging to the global optimum since it is not guaranteed that $\true{G}$ lies within the attraction region of the global optimum.
\end{remark}

@@

%$\hat G_\mathrm{trunc}$ and $\hat G_\mathrm{BTLS}$ are discussed later on.

The success rate $\eta$ is expressed mathematically as a probability function, consistent with Conjecture \ref{conj1}, \emph{viz}:
%\JL{in agreement with assumption \ref{assumption_G0hat_is_global_optimum}} \emph{viz}:
\begin{align}
\eta=\Prob{\hat G_\bullet=\hat G_0}
\end{align}
In practice, and since the iterative algorithm usually does not reach the local optimum precisely, the above definition is relaxed to the form
\begin{align}\label{eq:successrateTol}
\eta=\Prob{ \norm{\hat G_\bullet-\hat G_0} < tol}
\end{align}
with $tol$ a numerical tolerance that will be specified later on.
\TODO{Johan: beter een relatief criterium gebruiken (delen door $\norm{\true{G}}$)}

@@

%\begin{align}
%p(\hat G_x=\hat G_\circ) %G_0(q)= B(q)/A(q)
%\end{align}

The distance measure used in equation \eqref{eq:successrateTol} is defined, for discrete time, as
\begin{align}
\|G\|_2 = \sqrt{\frac{1}{2\pi}\int_0^{2\pi} |G(e^{-j\omega})|^2\ \mathrm{d}\omega}
\end{align}
 which, in practice, is computed by using the adaptive global quadrature algorithm provided by the MATLAB function \code{integral}.
%\comment{EG: The exact implementation is in the L2Norm function. Basically, either numerical or symbolic integration can be used (as our models are parametric), but both yield equally workable results (cfr. testDistance). I picked a full numerical approach as the symbolic one doesn't always work on my computer.}
%\JL{The success rate in \eqref{eq:successrateTol} will be estimated via Monte Carlo simulations, further\ML{/later} on.}
The success rate in equation \eqref{eq:successrateTol} is estimated via Monte Carlo simulations in  Section \ref{se:CompuSR}.

@@

The input excitation and the disturbing output noise were $N=1024$ samples of white Gaussian noise such that and an SNR of $20 \unit{dB}$ was attained at the output.
Note that due to $\norm[2]{\true{G}}=1$, the validation distance $\norm{\model{G} - \true{G}}$ is exactly the relative \gls{RMS} estimation error of the transfer function.

@@

\subsection{Observations}
The transfer functions are shown in \figref{fig:bodeplots} while the empirical cumulative validation distance is shown in \figref{fig:distancesStress}.
In \tabref{tbl:init:stresstest}, also the success rates per method are given when a tolerance $tol = 0.02$ is used when success is determined as $D_{\bullet} = \norm{\model{\bullet} - \true{G}} < tol$.

@@

\TODO{describe settings for the experiment: $N$, etc.}

The observed timings are shown in \TODO{tableref}.
\TODO{discuss timings}

\TODO{table summary}

\subsection{Asymptotic runtime}
For the asymptotic runtime, we are mainly interested in how the runtime of the smoothers scale with the size of the dataset, i.e. the number of samples $N$, and the model complexity $n_{\theta}$.

@@

The \gls{LPM} itself solves $N$ linear systems of small dimensions ($2N_W + 1$ equations and a few degrees of freedom), hence the overall runtime will be $\bigO{N \cdot N_W^3}$ since solving a linear system requires $\bigO{n^3}$ operations in general~\citep{Golub1996}.
The truncation of the impulse response relies on linear regression which takes $\bigO{n_{\theta}^2 N}$ operations.
Overall, this means that the time-truncated \gls{LPM} operates in $\bigO{N}$ since both $n_{\theta}$ and $N_W$ are typically small.

Since the \gls{RFIR} relies on fitting a \gls{FIR} filter to $N$ datapoints, this relies on inverting a matrix with largest dimension $N$. 
Using general methods, this is an operations that requires $\bigO{N^3}$ time.

It can be seen that the local modeling methods scale more favorably than e.g. \gls{RFIR}.

>>>>

\begin{algorithm}
\caption{Levenberg-Marquardt~\citep{Marquardt1963}, \citep[Sec. 9.L.4]{Pintelon2012}}\label{LMalgo}
\begin{algorithmic}[1]
  \Require Cost function \eqref{eq:MLEcf} is rewritten as $V(\theta) = \epsilon(\theta)^{\TT} \epsilon(\theta)$. 
\Function{LevenbergMarquardt}{$\epsilon(\theta),  \theta^{\mathrm{init}}$}
   \State $\atIter[0]{\theta} \gets \theta^{\mathrm{init}}$
   \Comment{$\atIter[i]{X}$ denotes $X$ at iteration $i$.}
   \For{$i$ \textbf{in} $1 \to \infty$}
      \State $U \, \Sigma \, W^{\TT} \gets \code{svd}\left( \frac{\partial \epsilon(\atIter[i-1]{\theta})}{\partial \theta}\right)$ 
        \Comment{Singular value decomposition of Jacobian}
      % \State $
      %                  \text{Denote }\Sigma \equiv 
      %                  \left[ \begin{matrix} 
      %                  \sigma_1         & \deemph{0} & \deemph{\cdots} &           & \deemph{0}      \\
      %                  \deemph{0}      & \sigma_2    &                   &           &                   \\
      %                  \deemph{\vdots} &              & \ddots            &           & \deemph{\vdots} \\
      %                                    &              &                   & \sigma_n &                   \\
      %                   \deemph{0}      &              & \deemph{\cdots} &           & \deemph{0}      
      %                   \end{matrix}\right]
      %                $
      % \State \textbf{if} $i=1$ \textbf{ then} $\lambda \gets \max(\sigma) / 100$
      \If{$\lambda$ is undefined}
        \State $\lambda \gets \max(\Set{\Sigma_{11}, \ldots, \Sigma_{nn}})/100$
      \EndIf
      \State $\Sigma_{kk} \gets \frac{\Sigma_{kk}}{(\Sigma_{kk}^2 + \lambda^2)} \quad \forall k \in \Set{1, \ldots, n}$
      \State $\delta\theta \gets - W  \Sigma^{\TT}  U^{\TT} \epsilon(\atIter[i-1]{\theta})$
      \State $\atIter[i]{\theta} \gets \frac{(\atIter[i-1]{\theta} + \delta\theta) }{ \norm[2]{\atIter[i-1]{\theta} + \delta\theta} }$
      \If{$V(\atIter[i]{\theta}) > V(\atIter[i-1]{\theta})$} \Comment{Current step is a deterioration}
         \State $\atIter[i]{\theta} \gets \atIter[i-1]{\theta}$ \Comment{Restart loop from previous estimate}
          \State $\lambda \gets 10 \lambda$ 
      \Else
          \State $\lambda \gets 0.4 \lambda$
      \EndIf
      \If {$\norm[2]{\delta\theta} < n_{\theta}  \cdot 10^{-6} \norm[2]{\atIter[i]{\theta}}$}
          \State \textbf{return} $\hat{\theta} \gets \atIter[i]{\theta}$
      \EndIf
   \EndFor
\EndFunction
\end{algorithmic}
\end{algorithm}

@@

%\JL{
The \gls{RFIR} estimator is formulated in the time domain. 
It estimates the impulse response of a discrete time system as the minimizer of the following regularized least squares objective function:
\begin{align}\label{eq:hRFIRdef}
\hat g_{\mathrm{RFIR}} &= \argmin_{g} \norm{y - g \ast u }^2 + \sigma^2 g^{\TT}P^{-1}g
\end{align}
where $g$ is the vectorized impulse response $g(t)$, with $t = 0,1,\cdots,n_h - 1$, assuming that the impulse response is $n_g$ samples long. 
Furthermore, $g\ast u$ is the convolution of $g$ with the input signal $u$, and $P\in \mathbb{R}^{n_g\times n_g}$ is the kernel matrix. 
Note that \eqref{eq:hRFIRdef} is quadratic in $g$, such that $\hat g_{\mathrm{RFIR}}$ can be computed analytically in a single step.
The kernel matrix $P$ embodies prior knowledge on the system to be estimated. 
Here, the \gls{DCkernel} is used. 
Specifically, the element at $t_1,t_2$ of $P$ is given by
\begin{equation}
P(\alpha,\beta)_{t_1,t_2} = e^{-\alpha|t_1 - t_2|}e^{-\beta(t_1 + t_2)/2}
\end{equation}
 for $t_1,t_2 \in \left\{0,1,\cdots,n_h - 1\right\}$ which makes the estimated impulse response to be an exponentially decaying function of $t$ with decay rate $\beta^{-1}$, and correlation length $\alpha^{-1}$. 
 The latter \emph{hyperparameters} $\alpha$, $\beta$ and $\sigma$ are determined using Empirical Bayes, i.e. as the maximizers of the \gls{LML} of the measured output signal:
\begin{align}
\mathrm{LML}(y) = -y^{\TT}\Sigma(\alpha,\beta)^{-1}y - \log |\Sigma(\alpha,\beta)| \text{,}
\end{align}
where $\Sigma(\alpha,\beta, \sigma) = \sigma^2 \I + \phi^{\TT}P(\alpha,\beta)\phi$ and $\phi$ is a Toeplitz matrix constructed with $u$. 
This problem is solved using \code{fmincon} in \MATLAB.

@@

Formally, let $\model{\bullet}$ be the final parametric estimate of the system, where the subscript $\bullet$ denotes the methods (from left to right in Fig.~\ref{fig:flowgraph}) when an initial estimate $\model[init]{\bullet}$ is used, \emph{viz}:
%\comment{JL:be consequent with the orders (and refer to the specific branches in the flowchart)}
\begin{itemize}
\item 
$\model{\trueSymbol}$ via the true model $\true{G}$ as an initial estimate,
\item
$\model{exist}$ is obtained via GTLS and BTLS,
\item
$\model{trunc}$ by the use of the LPM with truncation as an initial estimate,
\item
$\model{RFIR}$, initialized by means of the RFIR method. 
\end{itemize}

@@

\begin{conjecture}\label{conj1}
The true model $\true{G}$ as an initial estimate is the best possible initial estimate one can use for the nonlinear optimization algorithm (the leftmost path in \figref{fig:flowgraph}) and will allow the optimization to converge to the \emph{best local optimum}, i.e. $\model{\trueSymbol}$.
\end{conjecture}
\begin{remark}
The use of $\true{G}$ as an initial estimation not necessarily entails in converging to the global optimum since it is not guaranteed that $\true{G}$ lies within the attraction region of the global optimum.
\end{remark}

@@

The success rate $\eta$ is expressed mathematically as a probability function, consistent with Conjecture \ref{conj1}, \emph{viz}:
\begin{equation}
\eta_{\bullet}=\Prob{\model{\bullet}=\model{\trueSymbol}}
\end{equation}
In practice, and since the iterative algorithm usually does not reach the local optimum precisely, the above definition is relaxed to the form
\begin{equation}\label{eq:successrateTol}
\eta_{\bullet} \isdef \Prob{ \norm[2]{\model{\bullet} - \model{\trueSymbol}} < tol}
\end{equation}
with $tol$ a numerical tolerance that will be specified later on.
\begin{remark}
For an automated approach, it is better to define the success rate in terms of relative errors on the transfer function, i.e.
\begin{equation}
\eta_{\bullet} = \Prob{ \norm[2]{\model{\bullet}-\model{\trueSymbol}} < rel.tol  \norm[2]{\true{G}}}
\text{.}
\end{equation}
\end{remark}
\begin{remark}
In this chapter, the absolute criterion is used.
However, the results are equivalent for a relative criterion when the separation between successful and failed estimates is large since then observed success rate $\eta$ is only mildly sensitive towards the tolerance $tol$ (or $rel.tol$) when the tolerance is chosen with care.
Consequently, one can easily determine the equivalent relative tolerance from the absolute one using $tol = rel.tol \norm[2]{\true{G}}$.
\end{remark}

@@

The distance measure used in equation \eqref{eq:successrateTol} is defined as
\begin{align}
\norm[2]{G(z)} &\isdef \sqrt{\frac{1}{2\pi}\int_0^{2\pi} |G(e^{-j\omega})|^2\ \mathrm{d}\omega}& \text{ for discrete time,}\\
\norm[2]{G(s)} &\isdef \sqrt{\frac{1}{2\pi}\int_{-\infty}^{+\infty} |G(j\omega)|^2\ \mathrm{d}\omega}& \text{ for continuous time}
\end{align}
 which, in practice, is computed by using the adaptive global quadrature algorithm provided by the MATLAB function \code{integral}.
%\comment{EG: The exact implementation is in the L2Norm function. Basically, either numerical or symbolic integration can be used (as our models are parametric), but both yield equally workable results (cfr. testDistance). I picked a full numerical approach as the symbolic one doesn't always work on my computer.}
%\JL{The success rate in \eqref{eq:successrateTol} will be estimated via Monte Carlo simulations, further\ML{/later} on.}
The success rate in equation \eqref{eq:successrateTol} is estimated via Monte Carlo simulations in  Section \ref{se:CompuSR}.

@@

The input excitation and the disturbing output noise were $N=1024$ samples of white Gaussian noise such that and an \gls{SNR} of $20 \unit{dB}$ was attained at the output.
Note that due to $\norm[2]{\true{G}}=1$, the validation distance $\norm[2]{\model{\bullet} - \true{G}}$ is exactly the relative \gls{RMS} estimation error of the transfer function.

@@

\subsection{Observations}
The transfer functions are shown in \figref{fig:bodeplots} while the empirical cumulative validation distance is shown in \figref{fig:distancesStress}.
In \tabref{tbl:init:stresstest}, also the success rates per method are given when a tolerance $tol = 0.02$ is used when success is determined as $D_{\bullet} = \norm[2]{\model{\bullet} - \true{G}} < tol$.
This is equivalent to the relative criterion of success since $\norm[2]{\true{G}} = 1$ for all systems.

@@

To measure the timing of the different methods, essentially the same settings were used as in \secref{se:Demo}: the systems from equations \eqref{eq:systemundertest} and \eqref{eq:systundertest-20dB} were simulated such that $N_{3\unit{dB}} \in \Set{36,48}$ and $\SNR = 0 \unit{dB}$.
For each of the branches in \figref{fig:flowgraph}, three different timings are recorded (when applicable):
\begin{itemize}
  \item $t_{\mathrm{smooth}}$ is the time it takes to perform the smoothing (all blocks before \gls{GTLS}/\gls{BTLS}),
  \item $t_{\mathrm{init}}$ is the time it takes to fit $\model[init]{\bullet}$, and
  \item $t_{\mathrm{final}}$ is the time it takes to fit $\model{\bullet}$.
\end{itemize}
The median timings as returned by \code{timeit} are reported in \tabref{tbl:init:timing}.

\begin{table}
  \centering
  \centering
  \caption{Observed timing of the different estimation steps.}
% \input{\thisDir/table2.tex}
\pgfplotstabletypeset[precision=2,zerofill=true]{
Q  NBW  method  tsmooth    tinit  tfinal
 6  36  \model{true}    nan     nan     0.197034 
 6  36  \model{exist}   nan     nan     0.159937 
 6  36  \model{trunc}   0.745073    0.0623485   0.163107 
 6  36  \model{RFIR}    6.79873     0.0774866   0.175263 
 6  48  \model{true}    nan     nan     0.209216 
 6  48  \model{exist}   nan     nan     0.206823 
 6  48  \model{trunc}   1.00383     0.0902347   0.208173 
 6  48  \model{RFIR}    6.18632     0.0910651   0.221194 
20  36  \model{true}    nan     nan     0.445936 
20  36  \model{exist}   nan     nan     0.429752 
20  36  \model{trunc}   4.83667     0.225876    0.454757 
20  36  \model{RFIR}    6.92575     0.253981    0.482431 
20  48  \model{true}    nan     nan     0.467081 
20  48  \model{exist}   nan     nan     0.457577 
20  48  \model{trunc}   6.59726     0.312937    0.461114 
20  48  \model{RFIR}    8.05168     0.312297    0.468905 
}
\label{tbl:init:timing}

\TODO{fix pgfplotstable formatting}
\end{table}

From the timings in \tabref{tbl:init:timing}, it can be seen that the smoothers require a considerable amount of time that overshadows the fitting time.
However, it should be noted that all these implementations rely on code that has not been optimized for performance.
As such it is not possible to draw conclusions about the performance one may expect from performance-optimized implementations one would use in a commercial toolbox.
In particular the \gls{RFIR} smoother takes an exorbitant amount of time.
The fact that for small problem sizes (top of the table) the runtime is only slightly shorter than for the larger problems (bottom of the table), suggests that there is a considerable fixed overhead in the implementation we used.
Particularly, the construction of the \gls{DCkernel} matrix happens to be the culprit for these long execution times.
The truncated \gls{LPM}, on the other hand, requires a more reasonable amount of time for the short data lengths.
For longer datasets, it appears that the \code{kron} function is one of the major culprits for the long runtimes of the \gls{LPM}.

\subsection{Asymptotic runtime}
For the asymptotic runtime, we are mainly interested in how the runtime of the smoothers scale with the size of the dataset, i.e. the number of samples $N$, and the model complexity $n_{\theta}$ of the smoother.

@@

The \gls{LPM} itself solves $N$ linear systems of small dimensions ($2N_W + 1$ equations and a few degrees of freedom, i.e. $n_{\theta} \leq 2 N_W + 1$), hence the overall runtime will be $\bigO{N \cdot N_W^3}$ since solving a linear regression problem with $C$ parameters and $D$ datapoints takes $\bigO{C^3  + D C^2}$ operations\footnote{See http://math.stackexchange.com/questions/84495/computational-complexity-of-least-square-regression-operation}.
The truncation of the impulse response relies on linear regression which takes $\bigO{N}$ operations since only $3$ parameters are estimated during this step.
Overall, this means that the time-truncated \gls{LPM} operates in $\bigO{N n_{\theta}^{3}}$

The \gls{RFIR} relies on fitting a \gls{FIR} filter with $n_{\theta} = n_g$ taps to $N$ datapoints.
Using the same logic as above, this requires $\bigO{N n_{g}^2 + n_g^3}$ operations.

The computational complexity  of both methods scales linearly in the length of the dataset.
However, since the required length $n_g$ of a \gls{FIR} filter is typically a lot more (e.g. $200$ in this chapter) than the number of local parameters (or bandwidth) of the \gls{LPM} (e.g. $N_W = 3$), it can be seen that eventually the \gls{RFIR} method will scale less favorably for the model complexity of the smoother.
Intuitively, the local modeling methods benefit from their locality since that enables them to be flexible without a huge amount of parameters.

### 2016-02-16 ch05-initvals/styles.inc.tex
Table with different stress test cases
Clean up special histogram figure
Timing of initvals completed

\pgfplotstableset{
	%zerofill=true,
	after row=[3pt],
	assign column name/.code={%
        \pgfkeyssetvalue{/pgfplots/table/column name}{\multicolumn{1}{c}{\multirow{2}{*}{#1}} }%
    },
	columns/method/.style={string type,column name={\shortstack{\textsc{Method}\\\phantom{0}}}}, 
	columns/contribution/.style={column name={\textsc{Contribution}}},
	columns/P000/.style={column type=r,column name={\shortstack[r]{\textsc{Min.}\\{$0\%$}}}},
	columns/P025/.style={column type=r,column name={\shortstack[r]{\vphantom{?}\\\textsc{$25\%$}}}},
	columns/P050/.style={column type=r,column name={\shortstack[r]{\textsc{Median}\\{$50\%$}}}},
	columns/P075/.style={column type=r,column name={\shortstack[r]{\vphantom{?}\\\textsc{$75\%$ }}}},
	columns/P100/.style={column type=r,column name={\shortstack[r]{\textsc{Max.}\\{$100\%$}}}},
	columns/contribution/.style={column name={\shortstack[r]{\textsc{Contribution}\\ \vphantom{0}}},
	postproc cell content/.append code={
            %\ifnum1=\pgfplotstablepartno
                \pgfkeysalso{@cell content/.add={}{\%}}%
            %\fi
        },
	},
	every head row/.style={before row=\toprule, after row={\\\midrule}},
    every last row/.style={after row=\bottomrule}
}

>>>>

\pgfplotstableset{%
	%zerofill=true,
	after row=[3pt],
                  clear infinite,
	assign column name/.code={%
        \pgfkeyssetvalue{/pgfplots/table/column name}{\multicolumn{1}{c}{\multirow{2}{*}{#1}} }%
    },
	columns/method/.style={string type,column name={\shortstack{\textsc{Method}\\\phantom{0}}}},
	columns/contribution/.style={column name={\textsc{Contribution}}},
	columns/P000/.style={column type=r,column name={\shortstack[r]{\textsc{Min.}\\{$0\%$}}}},
	columns/P025/.style={column type=r,column name={\shortstack[r]{\vphantom{?}\\\textsc{$25\%$}}}},
	columns/P050/.style={column type=r,column name={\shortstack[r]{\textsc{Median}\\{$50\%$}}}},
	columns/P075/.style={column type=r,column name={\shortstack[r]{\vphantom{?}\\\textsc{$75\%$ }}}},
	columns/P100/.style={column type=r,column name={\shortstack[r]{\textsc{Max.}\\{$100\%$}}}},
                  columns/Q/.style={column type=r,column name={\shortstack[r]{\textsc{$Q$.}\\{$\unit{dB}$}}}},
                  columns/NBW/.style={column type=r,column name={\shortstack[r]{\textsc{$N_{\mathrm{3dB}}$.}\\{}}}},
                  columns/tsmooth/.style={column type=r,column name={X}},
                  columns/tinit/.style={column type=r,column name={\shortstack[r]{\textsc{$t_{\mathrm{init}}$.}\\{$\unit{s}$}}}},
                  columns/tfinal/.style={column type=r,column name={\shortstack[r]{\textsc{$t_{\mathrm{final}}$.}\\{$\unit{s}$}}}},
	columns/contribution/.style={column name={\shortstack[r]{\textsc{Contribution}\\ \vphantom{0}}},
	postproc cell content/.append code={
            %\ifnum1=\pgfplotstablepartno
                \pgfkeysalso{@cell content/.add={}{\%}}%
            %\fi
        },
	},
	every head row/.style={before row=\toprule, after row={\\\midrule}},
    every last row/.style={after row=\bottomrule}
}
